Formalizing Stack Safety as a Security Property

### 2021-07-09 submission3/main.tex
Filled in testing

We test {\em Lazy Per-activation Tagging and Clearing}, in which
each activation is tagged uniquely, and find that it obeys stepwise
confidentiality and observational integrity. To round out our mutations testing
we also check an equivalent to {\em LOAD\_NO\_CHECK} and a version where
stores succeed but fail to propagate the PC tag, {\em STORE\_NO\_UPDATE}.

\begin{table}[]
\centering
\begin{tabular}{c|c|c|c}
        Bug & Property Violated & MTTF (s) & Tests \\
  \hline
        {\em PER\_DEPTH\_TAG} & Observational Integrity & 70 & \\
        {\em LOAD\_NO\_CHECK}  & Observational Integrity & 23.5 & 12 \\
        {\em LOAD\_NO\_CHECK}  & Confidentiality & 19.2 & 695.5 \\
        {\em STORE\_NO\_UPDATE} & Observational Integrity & 80.6 &  \\
        {\em STORE\_NO\_UPDATE} & Confidentiality & 4.9 & 88.5 \\
\end{tabular}
\vspace*{1em}
\caption{MTTF for finding bugs in erroneous policy enforcement mechanisms}
\vspace*{-2em}
\label{tab:lazy-bug-table}
\end{table}

>>>>

We test {\em Lazy Per-activation Tagging and Clearing}, in which
each activation is tagged uniquely, and find that it obeys stepwise
confidentiality and observational integrity. To round out our mutations testing
we also check an equivalent to {\em LOAD\_NO\_CHECK} and a version where
stores succeed but fail to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
taking twice as long to catch as the next longest.

\begin{table}[]
\centering
\begin{tabular}{c|c|c|c}
        Bug & Property Violated & MTTF (s) & Tests \\
  \hline
        {\em PER\_DEPTH\_TAG} & Observational Integrity & 189.7 & 8342.5  \\
        {\em LOAD\_NO\_CHECK}  & Observational Integrity & 23.5 & 12.0 \\
        {\em LOAD\_NO\_CHECK}  & Confidentiality & 19.2 & 695.5 \\
        {\em STORE\_NO\_UPDATE} & Observational Integrity & 70 & 80.6  \\
        {\em STORE\_NO\_UPDATE} & Confidentiality & 4.9 & 88.5 \\
\end{tabular}
\vspace*{1em}
\caption{MTTF for finding bugs in erroneous policy enforcement mechanisms}
\vspace*{-2em}
\label{tab:lazy-bug-table}
\end{table}
